Union and intersection contracts are hard, actually

### 2021-06-10 paper.tex
Typo

Efficiency is also affected another way: each time a function with a
contract attached is applied, the whole \emph{context} must be
traverse to check for a compatibility property.

>>>>

Efficiency is also affected another way: each time a function with a
contract attached is applied, the whole \emph{context} must be
traversed to check for a compatibility property.
